---
title: "TPS Analysis Technical Appendix"
author: "Andrew Nalundasan, Lynna Tran, Rosalie Sherry, Vishaal Diwan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Export this into a word document and do formatting manually for final .docx version
## Export to PDF if needed since don't know how to make formatting updates (font, spacing, etc.) to templates

### Section Header if needed

1. Executive Summary

2. Introduction 

+ Tarragon Property Services - Company Profile

    - Blurbs about what the property does

3. Problem Statement

    - Problem statement here
    
4. Literature Review

    + perhaps move this to the end?
    
5. Description of Data

    + Define the dataset, explain how it is structured and its value.
    
6. Data Preprocessing

    + Define any processes around data preprocessing, if applicable.
    + manual work done in excel prior to reading into R
    + simple calculations made in R
    
7. Models and Evaluations

    + explain the models used and the evaluations chosen
    
8. Interpretations and Analysis

9. Discussion

10. Conclusion

11. References

+ Brownlee, J. (2020, August 18). Principal component analysis for dimensionality reduction in python. Machine Learning Mastery. Retrieved July 12, 2022, from https://builtin.com/data-science/step-step-explanation-principal-component-analysis
+ Gupta, P. (2017, November 16). Regularization in machine learning. Medium. Retrieved July 12, 2022, from https://towardsdatascience.com/regularization-in-machine-learning-76441ddcf99a
+ Wingate, R. (2020, August 10). Dimensionality reduction and PCA. Ryan Wingate. Retrieved July 12, 2022, from https://ryanwingate.com/intro-to-machine-learning/unsupervised/dimensionality-reduction-and-pca/


12. Appendix (Technical Appendix - include R code)

```{r}
# insert all code from technical_memo into this code chunk
```

