---
title: "TPS Analysis Technical Appendix"
author: "Andrew Nalundasan, Lynna Tran, Rosalie Sherry, Vishaal Diwan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: no
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load Libraries
```{r , hide=TRUE, include=FALSE}

library(readxl)  # to read in data
library(tidyverse)  
library(jtools)  # for export_summs
library(vtable)  # for vtable
library(dplyr)
library(lubridate) # to cast date-time datatypes
library(gridExtra)  # for grid arrange
library(janitor)  # for tabyl
library(writexl)
library(lubridate)
library(sqldf)



```


```{r Directory for Lynna}
##setwd("/Users/lynnatran/Documents/MSBA/Capstone Project/Repository/5510-DTC/02_rawdata")

```

# Load data

+ Data pre-processing occurred in excel using manual formatting
+ No complex wrangling anticipated
+ After verifying the raw data was formatted correctly, we read in the data

## Read-in Ledger Reports
```{r Read in Ledger reports}

ledger_balance <- read_excel("../02_raw_data/ledger/Ledger Beginning and Ending Balances.xlsx")
ledger_01 <- read_excel("../02_raw_data/ledger/CLEAN  54445 - MAILINGS AND NEWSLETTER.xlsx")
ledger_02 <- read_excel("../02_raw_data/ledger/CLEAN 54410 - MARKETING.xlsx")
ledger_03 <- read_excel("../02_raw_data/ledger/CLEAN 54425 - WEBSITE EXPENSE.xlsx")
ledger_04 <- read_excel("../02_raw_data/ledger/CLEAN 54430 - BRANDING EXPENSE.xlsx")
ledger_05 <- read_excel("../02_raw_data/ledger/CLEAN 54435 - PUBLIC RELATIONS.xlsx")
ledger_06 <- read_excel("../02_raw_data/ledger/CLEAN 54455 - TENANT RELATIONS.xlsx")
ledger_07 <- read_excel("../02_raw_data/ledger/CLEAN 54465 - BROCHURE AND BUSINESS CARDS.xlsx")
ledger_08 <- read_excel("../02_raw_data/ledger/CLEAN 54475 - DUES MEMBERSHIPS SUBSCRIPTIONS.xlsx")
ledger_09 <- read_excel("../02_raw_data/ledger/CLEAN 54480 - INTERNET ADVERTISING.xlsx")
ledger_10 <- read_excel("../02_raw_data/ledger/CLEAN 54481 - INTERNET LISTING SERVICES.xlsx")
ledger_11 <- read_excel("../02_raw_data/ledger/CLEAN 54482 - SEO SERVICES.xlsx")
ledger_12 <- read_excel("../02_raw_data/ledger/CLEAN 54485 - SIGN POSTERS OTHER.xlsx")
ledger_13 <- read_excel("../02_raw_data/ledger/CLEAN 54490 - MODEL EXPENSE.xlsx")
ledger_14 <- read_excel("../02_raw_data/ledger/CLEAN 54495 - REFERRAL COMMISSIONS.xlsx")

```

```{r Adding LedgerAccount to Ledger tables}

ledger_01 <- ledger_01 %>% mutate(ledgerAccount = "Mailings")
ledger_02 <- ledger_02 %>% mutate(ledgerAccount = "Marketing")
ledger_03 <- ledger_03 %>% mutate(ledgerAccount = "Website Expense") 
ledger_04 <- ledger_04 %>% mutate(ledgerAccount = "Branding Expense")
ledger_05 <- ledger_05 %>% mutate(ledgerAccount = "Public Relations")
ledger_06 <- ledger_06 %>% mutate(ledgerAccount = "Tenant Relations")
ledger_07 <- ledger_07 %>% mutate(ledgerAccount = "Brochure")
ledger_08 <- ledger_08 %>% mutate(ledgerAccount = "Dues Memberships")
ledger_09 <- ledger_09 %>% mutate(ledgerAccount = "Internet Advertising")
ledger_10 <- ledger_10 %>% mutate(ledgerAccount = "Internet Listing")
ledger_11 <- ledger_11 %>% mutate(ledgerAccount = "SEO Services")
ledger_12 <- ledger_12 %>% mutate(ledgerAccount = "Signs Posters")
ledger_13 <- ledger_13 %>% mutate(ledgerAccount = "Model Expense")
ledger_14 <- ledger_14 %>% mutate(ledgerAccount = "Referral Comissions")

```


## Read-in Traffic Reports 
```{r  Read in Traffic Reports}

property_list <- read_excel("../02_raw_data/PROPERTY LIST.xlsx")
aspen <- read_excel("../02_rawdata/traffic/ASPEN TRAFFIC REPORT_cleean.xlsx")
aster <- read_excel("../02_rawdata/traffic/ASTER TRAFFIC REPORT_clean.xlsx")
beryl <- read_excel("../02_rawdata/traffic/BERYL TRAFFIC REPORT_clean.xlsx")
blacklake  <- read_excel("../02_rawdata/traffic/BLACK LAKE TRAFFIC REPORT_clean.xlsx")
boxcar  <- read_excel("../02_rawdata/traffic/BOXCAR TRAFFIC REPORT_clean.xlsx")
chinook  <- read_excel("../02_rawdata/traffic/CHINOOK TRAFFIC REPORT_clean.xlsx")
cobble  <- read_excel("../02_rawdata/traffic/COBBLE TRAFFIC REPORT_clean.xlsx")
dwell  <- read_excel("../02_rawdata/traffic/DWELL TRAFFIC REPORT_clean.xlsx")
edition  <- read_excel("../02_rawdata/traffic/EDITION TRAFFIC REPORT_clean.xlsx")
fourlakes  <- read_excel("../02_rawdata/traffic/FOUR LAKES TRAFFIC REPORT_clean.xlsx")
glacier1  <- read_excel("../02_rawdata/traffic/GLACIER TRAFFIC REPORT_clean.xlsx")
glacier2  <- read_excel("../02_rawdata/traffic/GLACIER II TRAFFIC REPORT_clean.xlsx")
monticello  <- read_excel("../02_rawdata/traffic/MONTICELLO TRAFFIC REPORT_clean.xlsx")
palermo  <- read_excel("../02_rawdata/traffic/PALERMO TRAFFIC REPORT_clean.xlsx")
renwood  <- read_excel("../02_rawdata/traffic/RENWOOD TRAFFIC REPORT_clean.xlsx")
riverside  <- read_excel("../02_rawdata/traffic/RIVERSIDE TRAFFIC REPORT_clean.xlsx")
sawyertrail1  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TRAFFIC REPORT_clean.xlsx")
sawyertrail2  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL II TRAFFIC REPORT_clean.xlsx")
sawyertrail_th1  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TOWNHOMES TRAFFIC REPORT_clean.xlsx")
sawyertrail_th2  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TOWNHOMES II TRAFFIC REPORT_clean.xlsx")
wacourtflat  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT FLATS TRAFFIC REPORT_clean.xlsx")
wacourtres  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT RESIDENTIAL TRAFFIC REPORT_clean.xlsx")
wacourtvillage  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT VILLAGE SQUARE TRAFFIC REPORT_clean.xlsx")

dwell <- dwell %>%
  mutate('Property Name' = case_when('Property Name' == "Dwell" ~ "dwell"))

```

# Joining Data

## Combine Ledger Reports 
```{r}
# pipeline to join all reports for base_1 datasets
ledger_base <- bind_rows(x = ledger_01, y = ledger_02)
ledger_base <- bind_rows(x = ledger_base, y = ledger_03)
ledger_base <- bind_rows(x = ledger_base, y = ledger_04)
ledger_base <- bind_rows(x = ledger_base, y = ledger_05)
ledger_base <- bind_rows(x = ledger_base, y = ledger_06)
ledger_base <- bind_rows(x = ledger_base, y = ledger_07)
ledger_base <- bind_rows(x = ledger_base, y = ledger_08)
ledger_base <- bind_rows(x = ledger_base, y = ledger_09)
ledger_base <- bind_rows(x = ledger_base, y = ledger_10)
ledger_base <- bind_rows(x = ledger_base, y = ledger_11)
ledger_base <- bind_rows(x = ledger_base, y = ledger_12)
ledger_base <- bind_rows(x = ledger_base, y = ledger_13)
ledger_base <- bind_rows(x = ledger_base, y = ledger_14)
summary(ledger_base)
vtable(ledger_base)
```


## Combine Traffic Reports 
```{r}
# pipeline to join all reports for base_1 datasets
trafficReportList <- bind_rows(aspen,aster, beryl, blacklake, boxcar, chinook, cobble,
                           dwell, edition, fourlakes, glacier1, glacier2, monticello,
                           palermo, renwood, riverside,sawyertrail_th1,    sawyertrail_th2,
                           sawyertrail1, sawyertrail2, wacourtflat, wacourtres, wacourtvillage)

summary(trafficReportList)
vtable(trafficReportList)
```

# Data Cleanup

## Rename Sources in TrafficReportList
```{r Rename sources in Traffic Report List, message=FALSE}

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Apartment list", "Apartment List") ~ "Apartmentlist.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "apartments.com" ~ "Apartments.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "Craigslist-Basic Ad" ~ "Craigslist"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Drive By/ Signage", "Driveby") ~ "Drive-by/Signage"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "apartments.com" ~ "Apartments.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Google Ads", "Google My Business", "Google PayPerClick (PPC)",
                       "Google PayPerClick(PPC)", "Google Plus") ~ "Google"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Other", "Other/Online",
                       "Other/Walk in", "Other/Walk-in") ~ "Other"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Zillow Network", "Zillow/Hotpads") ~ "Zillow"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Referral - Resident", "Referral- Resident",
                       "Referrals", "Resident Referral", "Employee Referral",
                       "Referral - Family Member") ~ "Referral"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Property website", "portal") ~ "Property Website"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Other tarragon property","Tarragon Website",  "Corporate Website") ~ "Corporate Website"
        ,TRUE ~ Source
        )
    )

table(trafficReportList$Source)
```

## Rename Status and Result/Reason in TrafficReportList

```{r Status and Result/ Reason}

trafficReportList <- trafficReportList %>%  rename("Result" = "Result/ Reason") 

trafficReportList <- trafficReportList %>% 
    mutate(Status = case_when(
         Status %in% c("Canceled Guest", "CanceledGuest") ~ "Canceled"
        ,TRUE ~ Status
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Apartment list" ~ "Apartment List",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Applicant grouping" ~ "Applicant Grouping",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Created by Lead2Lease (Unqualified)", 
                       "Criminal History (Unqualified)",
                       "Does not credit qualify (Unqualified)",
                       "Does not income qualify (Unqualified)",
                       "Found another apartment (Unqualified)",
                       "Not moving (Unqualified)", "Personal (Unqualified)",
                       "Pet (Unqualified)", "Screening process (Unqualified)",
                       "Screening Process (Unqualified)",
                       "Still looking / Undecided (Unqualified)",
                       "Timeframe Change (Unqualified)", 
                       "Too many occupants (Unqualified)", 
                       "Unqualified (Unqualified)") ~ "Unqualified",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Desired floorplan not avail", "Desired floorplan not availabl",
                       "Desired Floorplan not availabl") ~ "Desired Floorplan not avail"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Desired mone-in date not avail", 
                       "Desired move in date not avail",
                       "Desired move in date unavail",
                       "Desired Move in date unavail",
                       "Desired move-in date not avail",
                       "Desired Move-in date not avail",
                       "Desired Move-in Date not avail") ~ "Desired Move in date not avail"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Found another apartment" ~ "Found another Apartment"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Future / 30 days out", "Future / 30 Days out",
                       "Future / 30-days out", "Future/30 days out") ~ "Future / 30-Days Out"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Leased an Apartment" ~ "Leased"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Not moving" ~ "Not Moving"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Promote Roommate" ~ "Roommate"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Screening process" ~ "Screening Process"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Still looking / Undecided", "Still looking/ Undecided",
                       "Still Looking/ Undecided", "Still Looking/Undecided ",
                       "StillLooking/ Undecided", "Still Looking/Undecided") ~ "Still Looking / Undecided"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Timeframe change" ~ "Timeframe Change"
        ,TRUE ~ Result
        )
    )

trafficReportList$Result[is.na(trafficReportList$Result)] <- "Unknown"


table(trafficReportList$Result)
```

# Wrangle data

```{r}
trafficReportList <- trafficReportList %>% 
  mutate("Status" = as.factor(Status)) %>% 
  mutate("Source" = as.factor(Source)) %>% 
  mutate("Result" = as.factor(Result)) 


# this is resulting in NA's
# Can't change 'Event Date' to date type. Need help on this.
# as.Date("Event Date", format =  "%mm/%dd/%YYYY")


# recode Status vector
trafficReportList <- trafficReportList %>% 
  mutate(num_status = case_when(trafficReportList$Status == 'Resident' ~ 1,
                                trafficReportList$Status == 'Approved' ~ 1,
                                trafficReportList$Status == 'Prospect' ~ 0, 
                                trafficReportList$Status == 'Denied' ~ 0,
                                trafficReportList$Status == 'CanceledGuest' ~ 0,
                                trafficReportList$Status == 'Canceled Guest' ~ 0,
                                trafficReportList$Status == 'Canceled' ~ 0,
                                trafficReportList$Status == 'Applied' ~ 0)) 

# filter 'Source' to top hits
trafficReportList_top_source_result <- trafficReportList %>% 
  filter(Source %in% c("Apartmentlist.com", "CoStar Group", 'Drive-by/Signage', 
                       'Google', 'Office', 'Property Website', 
                       'RENTCAFE.com ILS', 'Zillow')) %>% 
  filter(Result %in% c("Apartment List","Desired move-in date not avail", 
                                "Duplicate", "Found another apartment",
                                "Leased", "Not Moving", "Nothing", "Online Lead",
                                "Personal", "Still looking / Undecided", "Took Application", "Unknown"))

```

```{r Add sources to the ledger_base}
##

write_xlsx(ledger_base, "../02_raw_data/LedgerSources/ledger_base")


sourceList <- unique(trafficReportList$Source)

source_df <- data_frame(sourceList)
write_xlsx(source_df, "../02_raw_data/LedgerSources/sourceList")

ledger_baseSource <- read.csv("../02_raw_data/LedgerSources/ledger_base_withsourcesCSV.csv")

```

```{r Ledger_base with dates}
ledger_baseDates <- ledger_baseSource

ledger_baseDates <- ledger_baseDates %>%
 mutate('Year' = (substring(ledger_baseDates$'Date', 0, 4))) %>%
 mutate('Month' = (substring(ledger_baseDates$'Date', 6, 7))) ##


ledger_baseDates <- ledger_baseDates %>%
 mutate('Season' = case_when(ledger_baseDates$Month == '01' ~ 'Q1-Winter',
                             ledger_baseDates$Month == '02' ~ 'Q1-Winter',
                             ledger_baseDates$Month == '03' ~ 'Q1-Winter',
                             ledger_baseDates$Month == '04' ~ 'Q2-Spring',
                             ledger_baseDates$Month == '05' ~ 'Q2-Spring',
                             ledger_baseDates$Month == '06' ~ 'Q2-Spring',
                             ledger_baseDates$Month == '07' ~ 'Q3-Summer',
                             ledger_baseDates$Month == '08' ~ 'Q3-Summer',
                             ledger_baseDates$Month == '09' ~ 'Q3-Summer',
                             ledger_baseDates$Month == '10' ~ 'Q4-Fall',
                             ledger_baseDates$Month == '11' ~ 'Q4-Fall',
                             ledger_baseDates$Month == '12' ~ 'Q4-Fall'
                             ))


```

```{r TrafficReportList with dates}


trafficReportDates <- trafficReportList %>%
 mutate('Year' = (substring(trafficReportList$'Event Date', 7, 11))) %>%
 mutate('Month' = (substring(trafficReportList$'Event Date', 1, 2))) 

trafficReportDates <- trafficReportDates %>%
 mutate('Season' = case_when(trafficReportDates$Month == '01' ~ 'Q1-Winter',
                             trafficReportDates$Month == '02' ~ 'Q1-Winter',
                             trafficReportDates$Month == '03' ~ 'Q1-Winter',
                             trafficReportDates$Month == '04' ~ 'Q2-Spring',
                             trafficReportDates$Month == '05' ~ 'Q2-Spring',
                             trafficReportDates$Month == '06' ~ 'Q2-Spring',
                             trafficReportDates$Month == '07' ~ 'Q3-Summer',
                             trafficReportDates$Month == '08' ~ 'Q3-Summer',
                             trafficReportDates$Month == '09' ~ 'Q3-Summer',
                             trafficReportDates$Month == '10' ~ 'Q4-Fall',
                             trafficReportDates$Month == '11' ~ 'Q4-Fall',
                             trafficReportDates$Month == '12' ~ 'Q4-Fall'
                             ))

```


# Base EDA Step 1: Uni-variate non-graphical EDA
```{r}
# top of the dataset and look each subset
head(trafficReportList)
```

+ data appears to be tidy

    + data in each column is of the same variable type
    + no duplicate columns
    + each row is an observation for the sale of a specific home
    
```{r}
# check variable table
vtable(trafficReportList)
```

+ Property Name - string
+ Unit type - string
+ Unit - string
+ Applicant/Prospect - string
+ Event Date - datetime
+ Source - Categorical
+ Status - Categorical
+ Result/ Reason - Categorical

```{r}
summary(trafficReportList)
```

**Comments**

+ can't tell much since all variables are strings

**Questions**

+ How to convert string to date type

# Base EDA Step 2: Uni-variate graphical EDA - Categorical

```{r}
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Source 
ggplot(data = trafficReportList_top_source_result, mapping = aes(x = Source)) +
  geom_bar() + 
  coord_flip(), 

# Status
ggplot(data = trafficReportList_top_source_result, mapping = aes(x = Status)) +
  geom_bar() + 
  coord_flip(),

# Result/ Reason
ggplot(data = trafficReportList_top_source_result, mapping = aes(x = Result)) + 
  geom_bar() + 
  coord_flip(),

ncol = 2 )
```

**Comments**

+ Too many factors for 'Source'
+ Need to filter to top 5
+ Too many factors for 'Result/Reason'
+ Need to filter to top 5

```{r}
trafficReportList %>% 
  tabyl(Source) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) %>%  # Total margins
  adorn_percentages(denominator = "all") %>%   # creates proportions
  adorn_rounding(2) 
```

**Comments**

+ top 10 Source: 

    + Apartmentlist.com
    + CoStar Group
    + Drive-by/Signage
    + Google
    + Office
    + Property Website
    + RENTCafe.com ILS
    + Zillow

```{r}
# find highest factors in 'Source' and 'Result/Reason' 

trafficReportList %>% 
  tabyl(Result) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) %>%  # Total margins
  adorn_percentages(denominator = "all") %>%   # creates proportions
  adorn_rounding(2) 

```

**Comments**

+ top 10 Result/Reason:

    + Apartment List
    + Desired move-in date not avail
    + Duplicate
    + Found another apartment
    + Leased an Apartment
    + Not Moving
    + Nothing
    + Online Lead
    + Personal
    + Still looking / Undecided
    + Took Application
    + Unknown



```{r}
cols <- c("Joined" = "#37c871", "Not Joined" = "#ff0000")

p <- trafficReportList %>% 
  ggplot(mapping = aes(x = `Status`))

p + geom_histogram(bins = 10, position = "dodge", stat = "count") + 
  scale_fill_manual(values = cols) +

  #aesthetics = "colour") +
  #scale_fill_manual(c("green", "red")) +
  labs(title = "Distribution of Status") + 
  theme(legend.position = "right") + 
  coord_flip()
```


**Comments**

### Categorical

```{r}
trafficReportList %>% 
  filter(Source == 'Apartmentlist.com') %>% 
  tabyl(Source, Status) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r}
grid.arrange(
  # tile graph on promo and flavor
  trafficReportList %>% 
  group_by(Source, Status) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(Source, Status)) + 
  geom_tile())
```

# Marketing Metrics 

## Grouping on Ledger by Source

```{r Group by ledger_baseSource}

ledgerSourceGroups <- ledger_baseSource %>% 
  select(Source) %>%
  tabyl(Source)

##summary(ledgerSourceGroups)
kable(ledgerSourceGroups)
```

## Grouping on the Traffic reports by source

```{r Group by TrafficReportList - Source}

trafficSourceGroups <- trafficReportList %>% 
  select(Source) %>%
  group_by(Source) %>%
  count(Source)

summary(trafficSourceGroups)
```
## Grouping on the Traffic reports data by Source and Status

```{r Group by TrafficReportList - Source, Status}
trafficReportList %>% 
  select(Source, Status) %>%
  tabyl(Source, Status)
```

## Grouping on the Traffic reports data by Year and Season

```{r Group by TrafficReportList - Dates}

trafficReportDates %>%
  select(Year) %>%
  tabyl(Year)

trafficReportDates %>%
  select(Season) %>%
  tabyl(Season)
```

## Grouping on the Traffic Property data

```{r Group by TrafficProperty}

## Joining Traffic Reports Data with Property List 

trafficProperty <- trafficReportList %>%
  left_join(property_list, by = c('Property Name' = 'Yardi Id Code'))


trafficProperty %>% 
  select('PROPERTY TYPE:') %>%
  tabyl('PROPERTY TYPE:')

trafficProperty %>% 
  select('LOCATION:') %>%
  tabyl('LOCATION:')

trafficProperty %>% 
  select('COUNTY:') %>%
  tabyl('COUNTY:')

```
# Cost per Lead Analysis

```{r Grouping by Source GL and Traffic Report}

GLSourceGrouping <- sqldf("
      select Source, count(Source) countSource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) TotalSpending
      from ledger_baseSource
      group by Source
      ")

kable(GLSourceGrouping)

TRSourceGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.CountLead as float)
                    end
                ) ResidentRate
     from 
        (select Source, count(Source) countLead,
          (select count(trp2.num_status) 
          from trafficReportList trp2
          where trp2.num_status = 1 and trp2.Source = trp1.Source )                 ResidentStatusCount
        from trafficReportList trp1
        group by Source) sq
      ")

kable(TRSourceGrouping)
```


## Getting Cost per Lead

```{r Getting Cost per Lead}


costPerLead <- GLSourceGrouping %>%
  inner_join(TRSourceGrouping, "Source") %>%
  mutate(costPerLead =   TotalSpending/countLead,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget =   TotalSpending - costForAllResidents) %>%
  select(Source, TotalSpending, countLead, ResidentStatusCount, ResidentRate, costPerLead, costForAllResidents, unallocatedBudget)

kable(costPerLead)
```

## Getting Cost per Lead by Year

```{r Grouping by Year}

GLYearGrouping <- sqldf("
      select Source, Year, count(Source) countSource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from ledger_baseDates
      group by Source, Year
      ")


TRYearGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.CountLead as float)
                    end
                ) ResidentRate
     from 
        (select Source, Year, count(Source) countLead,
          (select count(trp2.num_status) 
          from trafficReportDates trp2
          where trp2.num_status = 1 and trp2.Source = trp1.Source and trp2.Year =                 trp1.Year )                 ResidentStatusCount
        from trafficReportDates trp1
        group by Source, Year) sq
      ")

costPerYear <- GLYearGrouping %>%
  inner_join(TRYearGrouping, c("Source", "Year")) %>%
  mutate(costPerLead = DifferenceDebitCredit/countLead,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit) %>%
  select(Source, Year, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)


kable(costPerYear)


```

## Getting Cost per Lead by Season

```{r Grouping by Season}

GLSeasonGrouping <- sqldf("
      select Source, Season, count(Source) countSource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from ledger_baseDates
      group by Source, Season
      ")

TRSeasonGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.CountLead as float)
                    end
                ) ResidentRate
     from 
        (select Source, Season, count(Source) countLead,
          (select count(trp2.num_status) 
          from trafficReportDates trp2
          where trp2.num_status = 1 and trp2.Source = trp1.Source and trp2.Season =                 trp1.Season )                 ResidentStatusCount
        from trafficReportDates trp1
        group by Source, Season) sq
      ")

costPerSeason <- GLSeasonGrouping %>%
  inner_join(TRSeasonGrouping, c("Source", "Season")) %>%
  mutate(costPerLead = DifferenceDebitCredit/countLead,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit) %>%
  select(Source, Season, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)

kable(costPerSeason)
```

## Getting Cost per Lead by Property Type

```{r Grouping by Property Type }

GLPropertyType <- left_join(ledger_baseSource, property_list, by = c("Property"= "Yardi Id Code"))
                          

GLPropertyTypeGrouping <- sqldf("
      select [Property Type:] PropertyType ,count([Property Type:]) countPropertyType,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [Property Type:]
      ")


TRPropertyTypeGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadPropertyType as float)
                    end
                ) ResidentRate
     from 
        (select [Property Type:] PropertyType, count([Property Type:]) 
            countLeadPropertyType,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[Property Type:] = tp1.[Property Type:])                 ResidentStatusCount
        from trafficProperty tp1
        group by [Property Type:]) sq
      ")

costPerPropertyType <- GLPropertyTypeGrouping %>%
  inner_join(TRPropertyTypeGrouping, "PropertyType") %>%
    mutate(costPerLead = DifferenceDebitCredit/countLeadPropertyType,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit, countLead = countLeadPropertyType) %>%
  select(PropertyType, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)

kable(costPerPropertyType)
```

## Getting Cost per Lead by County

```{r Grouping by County }
                          
GLCountyGrouping <- sqldf("
      select [County:] County ,count([County:]) countCounty,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [County:]
      ")



TRCountyGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadCounty as float)
                    end
                ) ResidentRate
     from 
        (select [County:] County , count([County:]) countLeadCounty,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[County:] = tp1.[County:])                 ResidentStatusCount
        from trafficProperty tp1
        group by [County:]) sq
      ")


costPerCounty <- GLCountyGrouping %>%
  inner_join(TRCountyGrouping, "County") %>%
  mutate(costPerLead = DifferenceDebitCredit/countLeadCounty,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents)

kable(costPerCounty)
```



## Getting Cost per Lead by Location Type

```{r Grouping by Location }
                          
GLLocationGrouping <- sqldf("
      select [Location:] Location ,count([Location:]) countLocation,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [Location:]
      ")

TRLocationGrouping <- sqldf("
     select *, (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadLocation as float)
                    end
                ) ResidentRate
     from 
        (select [Location:] Location , count([Location:]) countLeadLocation,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[Location:] = tp1.[Location:])                 ResidentStatusCount
        from trafficProperty tp1
        group by [Location:]) sq
      ")


costPerLocation <- GLLocationGrouping %>%
  inner_join(TRLocationGrouping, "Location") %>%
  mutate(costPerLead = DifferenceDebitCredit/countLeadLocation,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents)   %>%
  rename(TotalSpending = DifferenceDebitCredit, countLead = countLeadLocation) %>%
  select(Location, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)


kable(costPerLocation)
```

# Cost per Lead Analysis by Property Characteristics 

## Getting Cost per Lead by Property Type and Source 


```{r}

GLPropertySourceGrouping <- sqldf("
      select [Property Type:] PropertyType, Source,  ([Property Type:] || Source) PS,
      count(*) countPropertySource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [Property Type:], Source
      ")


TRPropertySourceGrouping <- sqldf("
     select *, (sq.PropertyType || sq.Source) PS,
                (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadPropertySource as float)
                    end
                ) ResidentRate
     from 
        (select [Property Type:] PropertyType, Source,
        count(*) countLeadPropertySource,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[Property Type:] = tp1.[Property Type:] and tp2.Source = tp1.Source)                 ResidentStatusCount
        from trafficProperty tp1
        group by [Property Type:], Source) sq
      ")
costPerPropertySource <- GLPropertySourceGrouping %>%
  inner_join(TRPropertySourceGrouping, "PS") %>%
    mutate(costPerLead = DifferenceDebitCredit/countLeadPropertySource,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit, countLead = countLeadPropertySource,
         PropertyType = PropertyType.x, Source = Source.x) %>%
  select(PropertyType, Source, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)


kable(costPerPropertySource)
```


## Getting Cost per Lead by County and Source

```{r}
GLCountySourceGrouping <- sqldf("
      select [County:] County, Source,  ([County:] || Source) CS,
      count(*) countCountySource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [County:], Source
      ")
TRCountySourceGrouping <- sqldf("
     select *, (sq.County || sq.Source) CS,
                (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadCountySource as float)
                    end
                ) ResidentRate
     from 
        (select [County:] County, Source,
        count(*) countLeadCountySource,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[County:] = tp1.[County:] and tp2.Source = tp1.Source)                 ResidentStatusCount
        from trafficProperty tp1
        group by [County:], Source) sq
      ")
costPerCountySource <- GLCountySourceGrouping %>%
  inner_join(TRCountySourceGrouping, "CS") %>%
    mutate(costPerLead = DifferenceDebitCredit/countLeadCountySource,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit, countLead = countLeadCountySource,
         County = County.x, Source = Source.x) %>%
  select(County, Source, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)
kable(costPerCountySource)
```

## Getting Cost per Lead by Location Type and Source

```{r}
GLLocationSourceGrouping <- sqldf("
      select [Location:] Location, Source,  ([Location:] || Source) LS,
      count(*) countLocationSource,
      sum(Debit) sumDebit, sum(Credit) sumCredit,
      (sum(Debit) - sum(Credit)) DifferenceDebitCredit
      from GLPropertyType
      group by [Location:], Source
      ")
TRLocationSourceGrouping <- sqldf("
     select *, (sq.Location || sq.Source) LS,
                (case when sq.ResidentStatusCount = 0 then 0
                    else cast(sq.ResidentStatusCount as float)/
                         cast(sq.countLeadLocationSource as float)
                    end
                ) ResidentRate
     from 
        (select [Location:] Location, Source,
        count(*) countLeadLocationSource,
          (select count(tp2.num_status) 
          from trafficProperty tp2
          where tp2.num_status = 1 and tp2.[Location:] = tp1.[Location:] and tp2.Source = tp1.Source)                 ResidentStatusCount
        from trafficProperty tp1
        group by [Location:], Source) sq
      ")
costPerLocationSource <- GLLocationSourceGrouping %>%
  inner_join(TRLocationSourceGrouping, "LS") %>%
    mutate(costPerLead = DifferenceDebitCredit/countLeadLocationSource,
         costForAllResidents = costPerLead * ResidentStatusCount,
         unallocatedBudget = DifferenceDebitCredit - costForAllResidents) %>%
  rename(TotalSpending = DifferenceDebitCredit, countLead = countLeadLocationSource,
         Location = Location.x, Source = Source.x) %>%
  select(Location, Source, TotalSpending, countLead, ResidentStatusCount, ResidentRate,  costPerLead, costForAllResidents, unallocatedBudget)
kable(costPerLocationSource)
```

# Ratio of Status by Property Type 

```{r}
RatioStatus <- sqldf("
select *, cast(sq.CountCanceledLeads as float)/cast(sq.CountLeads as float) RatioStatus from
  (select  count(*) CountLeads, 
        (select count(*)
        from trafficProperty tp2 
        where tp2.Status = 'Canceled'
        ) CountCanceledLeads
        from trafficProperty tp1
        ) sq
      ")

kable(RatioStatus)


RatioStatusbyPropertyType <- sqldf("
select *, cast(sq.CountCanceledLeads as float)/cast(sq.CountLeads as float) RatioStatus from
  (select [Property Type:], count(*) CountLeads, 
        (select count(*)
        from trafficProperty tp2 
        where tp2.Status = 'Canceled' and tp2.[Property Type:] = tp1.[Property Type:]
        group by [Property Type:] ) CountCanceledLeads
        from trafficProperty tp1
        group by [Property Type:]) sq
      ")

kable(RatioStatusbyPropertyType)
```


# Regression Analysis

+ Independent variable: num_status (if they signed a lease or not)
+ Dependent variables: total spending (overall spending, by source, etc.)

What Source drives Status?
Ho: some activity does NOT impact the variable of interest
Ha: some activity DOES impact the variable of interest

Variable of interest <- Status

Ho: Source does not impact Status
Ha: Source impacts Status

What County drive Status??
Ho: County does not impact Status
Ha: County  impacts Status

## Join dataframes

```{r}
traffic_source_grouping <- trafficReportList %>% 
  right_join(GLSourceGrouping) %>% 
  drop_na()
```

```{r logistic regression}


reg_source <- glm(formula = num_status ~ Source, data = traffic_source_grouping)

export_summs(reg_source)
summary(reg_source)

```

**Comments**

+ Ho: Source does not impact Status

    + For every 1 unit increase in tenants signing a lease, there is a 0.11 unit increase in leases signed by Referral
        + This is significant at the 1% level
    + For every 1 unit increase in tenants signing a lease, there is a 0.04 unit increase in leases signed via Google
        + This is significant at the 5% level
    + We reject the null hypothesis due to a low p-value < 0.05

+ Ha: Source impacts Status

    + We fail to reject the alternative hypothesis due to low p-value < 0.05


```{r}
reg_county <- glm(formula = num_status ~ `COUNTY:`, data = trafficProperty)

export_summs(reg_county)
summary(reg_county)

```

**Comments**

+ Ho: County does not impact Status

    + For every 1 unit increase in a person signing a lease, there is a 0.08 unit association with leases being signed in Pierce County (compared to King county)
        + This is statistically significant at the 0.1 level
        + We reject the null hypothesis due to very low p-value (<2e-16)
    + There appears to be no effect in Thurston county compared to King County with p-value 0.509

+ Ha: County impacts Status

    + We fail to reject the alternative hypothesis because (<2e-16) > 0.05

# Export Dfs
```{r export dfs}


write_xlsx(traffic_source_grouping, "../02_raw_data/output/traffic_source_grouping.csv")

write_xlsx(trafficProperty, "../02_raw_data/output/trafficProperty.csv")

##Cost Per Lead Analysis

write_xlsx(costPerLead, "../02_raw_data/output/costPerLead.csv")

write_xlsx(costPerYear, "../02_raw_data/output/costPerYear.csv")

write_xlsx(costPerSeason, "../02_raw_data/output/costPerSeason.csv")

write_xlsx(costPerPropertyType, "../02_raw_data/output/costPerPropertyType.csv")

write_xlsx(costPerCounty, "../02_raw_data/output/costPerCounty.csv")

write_xlsx(costPerLocation, "../02_raw_data/output/costPerLocation.csv")




write_xlsx(costPerPropertySource, "../02_raw_data/output/costPerPropertySource.csv")

write_xlsx(costPerCountySource, "../02_raw_data/output/costPerCountySource.csv")

write_xlsx(costPerLocationSource, "../02_raw_data/output/costPerLocationSource.csv")

write_xlsx(RatioStatusbyPropertyType, "../02_raw_data/output/RatioStatusbyPropertyType.csv")


```



# Interpretation of results

+ We reject null hypothesis for both scenarios
+ Referrals in Pierce county have highest likelihood of leases being signed


# Conclusion

+ We are seeing the chances of tenants seeking residence in Pierce county are higher compared to King and Thurston county
+ 


# Future Research

+ Implement ML clustering algorithm to predict where residents will sign leases
+ Implement ML prediction model to predict if a lead results in a lease
+ Significance testing on unit type to help TPS determine types of properties to invest in 


```{r Getting Values for our Report}

TotalLeads <- sqldf('
  select *, (cast(sq.ResidentCount as float)/ 
            cast(sq.TotalLeads as float)) ResidentRate 
  from
  (select cast(count(*) as float) TotalLeads,
  (select cast(count(*) as float) from trafficReportList
  where num_status = 1) ResidentCount
  from trafficReportList) sq
  ')

```







