---
title: "TPS Analysis Technical Appendix"
author: "Andrew Nalundasan, Lynna Tran, Rosalie Sherry, Vishaal Diwan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load libraries
library(readxl)  # to read in data
library(tidyverse)  
library(jtools)  # for export_summs
library(vtable)  # for vtable
library(dplyr)
library(lubridate) # to cast date-time datatypes
library(gridExtra)  # for grid arrange
library(janitor)  # for tabyl
```


```{r Directory for Lynna}
setwd("/Users/lynnatran/Documents/MSBA/Capstone Project/Repository/5510-DTC/02_rawdata")


```

# Read-in the data

+ Data pre-processing occurred in excel using manual formatting
+ No complex wrangling anticipated
+ After verifying the raw data was formatted correctly, we read in the data

Read-in Ledger Reports
```{r}
# read-in data

ledger_balance <- read_excel("../02_raw_data/ledger/Ledger Beginning and Ending Balances.xlsx")
ledger_01 <- read_excel("../02_raw_data/ledger/CLEAN  54445 - MAILINGS AND NEWSLETTER.xlsx")
ledger_02 <- read_excel("../02_raw_data/ledger/CLEAN 54410 - MARKETING.xlsx")
ledger_03 <- read_excel("../02_raw_data/ledger/CLEAN 54425 - WEBSITE EXPENSE.xlsx")
ledger_04 <- read_excel("../02_raw_data/ledger/CLEAN 54430 - BRANDING EXPENSE.xlsx")
ledger_05 <- read_excel("../02_raw_data/ledger/CLEAN 54435 - PUBLIC RELATIONS.xlsx")
ledger_06 <- read_excel("../02_raw_data/ledger/CLEAN 54455 - TENANT RELATIONS.xlsx")
ledger_07 <- read_excel("../02_raw_data/ledger/CLEAN 54465 - BROCHURE AND BUSINESS CARDS.xlsx")
ledger_08 <- read_excel("../02_raw_data/ledger/CLEAN 54475 - DUES MEMBERSHIPS SUBSCRIPTIONS.xlsx")
ledger_09 <- read_excel("../02_raw_data/ledger/CLEAN 54480 - INTERNET ADVERTISING.xlsx")
ledger_10 <- read_excel("../02_raw_data/ledger/CLEAN 54481 - INTERNET LISTING SERVICES.xlsx")
ledger_11 <- read_excel("../02_raw_data/ledger/CLEAN 54482 - SEO SERVICES.xlsx")
ledger_12 <- read_excel("../02_raw_data/ledger/CLEAN 54485 - SIGN POSTERS OTHER.xlsx")
ledger_13 <- read_excel("../02_raw_data/ledger/CLEAN 54490 - MODEL EXPENSE.xlsx")
ledger_14 <- read_excel("../02_raw_data/ledger/CLEAN 54495 - REFERRAL COMMISSIONS.xlsx")

```


Read-in Traffic Reports 
```{r}
property_list <- read_excel("../02_rawdata/PROPERTY LIST_clean.xlsx")

aspen <- read_excel("../02_rawdata/traffic/ASPEN TRAFFIC REPORT_cleean.xlsx")
aster <- read_excel("../02_rawdata/traffic/ASTER TRAFFIC REPORT_clean.xlsx")
beryl <- read_excel("../02_rawdata/traffic/BERYL TRAFFIC REPORT_clean.xlsx")
blacklake  <- read_excel("../02_rawdata/traffic/BLACK LAKE TRAFFIC REPORT_clean.xlsx")
boxcar  <- read_excel("../02_rawdata/traffic/BOXCAR TRAFFIC REPORT_clean.xlsx")
chinook  <- read_excel("../02_rawdata/traffic/CHINOOK TRAFFIC REPORT_clean.xlsx")
cobble  <- read_excel("../02_rawdata/traffic/COBBLE TRAFFIC REPORT_clean.xlsx")
dwell  <- read_excel("../02_rawdata/traffic/DWELL TRAFFIC REPORT_clean.xlsx")
edition  <- read_excel("../02_rawdata/traffic/EDITION TRAFFIC REPORT_clean.xlsx")
fourlakes  <- read_excel("../02_rawdata/traffic/FOUR LAKES TRAFFIC REPORT_clean.xlsx")
glacier1  <- read_excel("../02_rawdata/traffic/GLACIER TRAFFIC REPORT_clean.xlsx")
glacier2  <- read_excel("../02_rawdata/traffic/GLACIER II TRAFFIC REPORT_clean.xlsx")
monticello  <- read_excel("../02_rawdata/traffic/MONTICELLO TRAFFIC REPORT_clean.xlsx")
palermo  <- read_excel("../02_rawdata/traffic/PALERMO TRAFFIC REPORT_clean.xlsx")
renwood  <- read_excel("../02_rawdata/traffic/RENWOOD TRAFFIC REPORT_clean.xlsx")
riverside  <- read_excel("../02_rawdata/traffic/RIVERSIDE TRAFFIC REPORT_clean.xlsx")
sawyertrail1  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TRAFFIC REPORT_clean.xlsx")
sawyertrail2  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL II TRAFFIC REPORT_clean.xlsx")
sawyertrail_th1  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TOWNHOMES TRAFFIC REPORT_clean.xlsx")
sawyertrail_th2  <- read_excel("../02_rawdata/traffic/SAWYER TRAIL TOWNHOMES II TRAFFIC REPORT_clean.xlsx")
wacourtflat  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT FLATS TRAFFIC REPORT_clean.xlsx")
wacourtres  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT RESIDENTIAL TRAFFIC REPORT_clean.xlsx")
wacourtvillage  <- read_excel("../02_rawdata/traffic/WASHINGTON COURT VILLAGE SQUARE TRAFFIC REPORT_clean.xlsx")

```


# Combine Ledger Reports 
```{r}
# pipeline to join all reports for base_1 datasets
ledger_base <- bind_rows(x = ledger_01, y = ledger_02)
ledger_base <- bind_rows(x = ledger_base, y = ledger_03)
ledger_base <- bind_rows(x = ledger_base, y = ledger_04)
ledger_base <- bind_rows(x = ledger_base, y = ledger_05)
ledger_base <- bind_rows(x = ledger_base, y = ledger_06)
ledger_base <- bind_rows(x = ledger_base, y = ledger_07)
ledger_base <- bind_rows(x = ledger_base, y = ledger_08)
ledger_base <- bind_rows(x = ledger_base, y = ledger_09)
ledger_base <- bind_rows(x = ledger_base, y = ledger_10)
ledger_base <- bind_rows(x = ledger_base, y = ledger_11)
ledger_base <- bind_rows(x = ledger_base, y = ledger_12)
ledger_base <- bind_rows(x = ledger_base, y = ledger_13)
ledger_base <- bind_rows(x = ledger_base, y = ledger_14)
summary(ledger_base)
vtable(ledger_base)
```


# Combine Traffic Reports 
```{r}
# pipeline to join all reports for base_1 datasets
trafficReportList <- bind_rows(aster, beryl, blacklake, boxcar, chinook, cobble,
                           dwell, edition, fourlakes, glacier1, glacier2, monticello,
                           palermo, renwood, riverside,sawyertrail_th1,    sawyertrail_th2,
                           sawyertrail1, sawyertrail2, wacourtflat, wacourtres, wacourtvillage)

summary(trafficReportList)
vtable(trafficReportList)
```

```{r}
# rename Source
library(dplyr)
trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Apartment list", "Apartment List") ~ "Apartmentlist.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "apartments.com" ~ "Apartments.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "Craigslist-Basic Ad" ~ "Craigslist"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Drive By/ Signage", "Driveby") ~ "Drive-by/Signage"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% "apartments.com" ~ "Apartments.com"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Google Ads", "Google My Business", "Google PayPerClick (PPC)",
                       "Google PayPerClick(PPC)", "Google Plus") ~ "Google"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Other", "Other tarragon property", "Other/Online",
                       "Other/Walk in", "Other/Walk-in") ~ "Other"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Zillow Network", "Zillow/Hotpads") ~ "Zillow"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Referral - Resident", "Referral- Resident",
                       "Referrals", "Resident Referral", "Employee Referral",
                       "Referral - Family Member") ~ "Referral"
        ,TRUE ~ Source
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Source = case_when(
         Source %in% c("Property website", "Corporate Website") ~ "Property Website"
        ,TRUE ~ Source
        )
    )

table(trafficReportList$Source)
```

```{r Status and Result/ Reason}
trafficReportList <- trafficReportList %>%  rename("Result" = "Result/ Reason") 

trafficReportList <- trafficReportList %>% 
    mutate(Status = case_when(
         Status %in% c("Canceled Guest", "CanceledGuest") ~ "Canceled"
        ,TRUE ~ Status
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Apartment list" ~ "Apartment List",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Applicant grouping" ~ "Applicant Grouping",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Created by Lead2Lease (Unqualified)", 
                       "Criminal History (Unqualified)",
                       "Does not credit qualify (Unqualified)",
                       "Does not income qualify (Unqualified)",
                       "Found another apartment (Unqualified)",
                       "Not moving (Unqualified)", "Personal (Unqualified)",
                       "Pet (Unqualified)", "Screening process (Unqualified)",
                       "Screening Process (Unqualified)",
                       "Still looking / Undecided (Unqualified)",
                       "Timeframe Change (Unqualified)", 
                       "Too many occupants (Unqualified)", 
                       "Unqualified (Unqualified)") ~ "Unqualified",
         TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Desired floorplan not avail", "Desired floorplan not availabl",
                       "Desired Floorplan not availabl") ~ "Desired Floorplan not avail"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Desired mone-in date not avail", 
                       "Desired move in date not avail",
                       "Desired move in date unavail",
                       "Desired Move in date unavail",
                       "Desired move-in date not avail",
                       "Desired Move-in date not avail",
                       "Desired Move-in Date not avail") ~ "Desired Move in date not avail"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Found another apartment" ~ "Found another Apartment"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Future / 30 days out", "Future / 30 Days out",
                       "Future / 30-days out", "Future/30 days out") ~ "Future / 30-Days Out"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Leased an Apartment" ~ "Leased"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Not moving" ~ "Not Moving"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Promote Roommate" ~ "Roommate"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Screening process" ~ "Screening Process"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% c("Still looking / Undecided", "Still looking/ Undecided",
                       "Still Looking/ Undecided", "Still Looking/Undecided ",
                       "StillLooking/ Undecided", "Still Looking/Undecided") ~ "Still Looking / Undecided"
        ,TRUE ~ Result
        )
    )

trafficReportList <- trafficReportList %>% 
    mutate(Result = case_when(
         Result %in% "Timeframe change" ~ "Timeframe Change"
        ,TRUE ~ Result
        )
    )

trafficReportList$Result[is.na(trafficReportList$Result)] <- "Unknown"


table(trafficReportList$Result)
```


# Wrangle data

```{r}
# all data in trafficReportList string type
# need to convert datatypes 

trafficReportList <- trafficReportList %>% 
  recode(`Source`, Resident = 1)

# Unit Type - Factor?

library(lubridate)

trafficReportList <- trafficReportList %>% 
  mutate("Status" = as.factor(Status)) %>% 
  mutate("Source" = as.factor(Source)) %>% 
  mutate("Result" = as.factor(Result)) 

%>% 
  mutate("Event Date" = as.Date("Event Date", format = "%m/%d/%Y"))

# this is resulting in NA's
# Can't change 'Event Date' to date type. Need help on this.
# as.Date("Event Date", format =  "%mm/%dd/%YYYY")



# filter 'Source' to top hits
trafficReportList <- trafficReportList %>% 
  filter(Source %in% c("Apartmentlist.com", "CoStar Group", 'Drive-by/Signage', 
                       'Google', 'Office', 'Property Website', 
                       'RENTCAFE.com ILS', 'Zillow')) %>% 
  filter(Result %in% c("Apartment List","Desired move-in date not avail", 
                                "Duplicate", "Found another apartment",
                                "Leased", "Not Moving", "Nothing", "Online Lead",
                                "Personal", "Still looking / Undecided", "Took Application", "Unknown"))
    

# recode Status vector
trafficReportList <- trafficReportList %>% 
  mutate(num_source = rename_wi(Source,
                         "Resident" = 1,
                         "Approved" = 1,
                         "Prospect" = 0, 
                         "Denied" = 0,
                         "CanceledGuest" = 0,
                         "Canceled Guest" = 0,
                         "Canceled" = 0,
                         "Applied" = 0)) 

trafficReportList$Source <- recode(trafficReportList$Source, Resident = 1)



```




# Base EDA Step 1: Uni-variate non-graphical EDA
```{r}
# top of the dataset and look each subset
head(trafficReportList)
```

+ data appears to be tidy

    + data in each column is of the same variable type
    + no duplicate columns
    + each row is an observation for the sale of a specific home
    
```{r}
# check variable table
vtable(trafficReportList)
```

+ Property Name - string
+ Unit type - string
+ Unit - string
+ Applicant/Prospect - string
+ Event Date - datetime
+ Source - Categorical
+ Status - Categorical
+ Result/ Reason - Categorical

```{r}
summary(trafficReportList)
```

**Comments**

+ can't tell much since all variables are strings

**Questions**

+ How to convert string to date type

# Base EDA Step 2: Uni-variate graphical EDA - Categorical

```{r}
# Only use bar graphs (like histogram) because nothing like boxplot for categorical variables
grid.arrange(

# Source 
ggplot(data = trafficReportList, mapping = aes(x = Source)) +
  geom_bar() + 
  coord_flip(), 

# Status
ggplot(data = trafficReportList, mapping = aes(x = Status)) +
  geom_bar() + 
  coord_flip(),

# Result/ Reason
ggplot(data = trafficReportList, mapping = aes(x = Result)) + 
  geom_bar() + 
  coord_flip(),

ncol = 2 )
```

**Comments**

+ Too many factors for 'Source'
+ Need to filter to top 5
+ Too many factors for 'Result/Reason'
+ Need to filter to top 5

```{r}
trafficReportList %>% 
  tabyl(Source) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) %>%  # Total margins
  adorn_percentages(denominator = "all") %>%   # creates proportions
  adorn_rounding(2) 
```

**Comments**

+ top 10 Source: 

    + Apartmentlist.com
    + CoStar Group
    + Drive-by/Signage
    + Google
    + Office
    + Property Website
    + RENTCafe.com ILS
    + Zillow

```{r}
# find highest factors in 'Source' and 'Result/Reason' 

trafficReportList %>% 
  tabyl(Result) %>% # creates table of counts
  adorn_totals(where = c("row", "col")) %>%  # Total margins
  adorn_percentages(denominator = "all") %>%   # creates proportions
  adorn_rounding(2) 

```

**Comments**

+ top 10 Result/Reason:

    + Apartment List
    + Desired move-in date not avail
    + Duplicate
    + Found another apartment
    + Leased an Apartment
    + Not Moving
    + Nothing
    + Online Lead
    + Personal
    + Still looking / Undecided
    + Took Application
    + Unknown



```{r}
cols <- c("Joined" = "#37c871", "Not Joined" = "#ff0000")

p <- trafficReportList %>% 
  ggplot(mapping = aes(x = `Status`))

p + geom_histogram(bins = 10, position = "dodge", stat = "count") + 
  scale_fill_manual(values = cols) +

  #aesthetics = "colour") +
  #scale_fill_manual(c("green", "red")) +
  labs(title = "Distribution of Status") + 
  theme(legend.position = "right") + 
  coord_flip()
```


**Comments**

### Categorical

```{r}
trafficReportList %>% 
  filter(Source == 'Apartmentlist.com') %>% 
  tabyl(Source, Status) %>%     # creates table of counts
  adorn_totals(where = c("row", "col")) %>%    # Total margins
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r}
grid.arrange(
  # tile graph on promo and flavor
  trafficReportList %>% 
  group_by(Source, Status) %>% 
  summarize(count = n()) %>% 
  ggplot(aes(Source, Status)) + 
  geom_tile())
```



# Regression Analysis

Ho: some activity does NOT impact the variable of interest

Ha: some activity DOES impact the variable of interest

Variable of interest <- Status

Ho: Source does not impact Status

Ha: Source impacts Status

```{r}

reg <- trafficReportList %>% 
  lm(Status ~ ., data = .)

export_summs(reg)

reg <- lm(formula = Status ~ Source, data = trafficReportList)

reg <- glm(formula = Status ~ Source, data = trafficReportList)

export_summs(reg)

media_int_reg <- lm(formula = Website ~ Gender, data = media_int)
```



+ pearson correlation
+ add in a correlation matrix just to make it look fancy
+ run some regressions


# Interpretation of results

+ highly correlated variables
+ lower correlated variables
+ regression analysis
+ interaction variables
+ interpretation of variability

# Conclusion



# Future Research









