---
title: "TPS Analysis Technical Appendix"
author: "Andrew Nalundasan, Lynna Tran, Rosalie Sherry, Vishaal Diwan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read-in the data

+ Data pre-processing occurred in excel using manual formatting
+ No complex wrangling anticipated
+ After verifying the raw data was formatted correctly, we read in the data

Read-in Ledger Reports
```{r}

```


Read-in Traffic Reports 
```{r}

```


# Combine Ledger Reports 
```{r}
# pipeline to join all reports for base_1 datasets
```


# Combine Traffic Reports 
```{r}
# pipeline to join all reports for base_1 datasets
```


# Machine Learning Algorithm

+ supervised learning for prediction model

    + variables that drive tenants to sign a lease
    + variables that deter tenants to sign a lease


+ pearson correlation
+ add in a correlation matrix just to make it look fancy
+ run some regressions


# Interpretation of results

+ highly correlated variables
+ lower correlated variables
+ regression analysis
+ interaction variables
+ interpretation of variability

# Conclusion



# Future Research









